Cellct analysis

### 2019-11-16 code/cellcount.Rmd
test
added in cell counts for missing samples, re organized a few things how I look at it

```{r heatmap, echo=F, fig.height=5, fig.width=3}
p <- cellct %>% 
  left_join(field, by="sample_id")

distinct(cellct, sample_id) %>% nrow()

short_names <- p %>% 
  mutate(short_morpho_name = case_when(morpho_sp=="Chlainomonas"~"Cr",
                                       morpho_sp=="Chloromonas cf. brevispina"~"Cb",
                                       morpho_sp=="Chloromonas cf. nivalis"~"Cn",
                                       morpho_sp=="Chloromonas krienitzii"~"Ck",
                                       morpho_sp=="Green cell"~"G",
                                       morpho_sp=="Other"~"O",
                                       morpho_sp=="Sanguina nivaloides"~"Sn"))

my_theme <- theme(axis.text.y=element_blank(),
                  axis.ticks.y=element_blank(), 
                  legend.position = "none")

cellct_heatmap <- ggplot(short_names, aes(y=alias %>% fct_reorder(elev_m), 
              x=short_morpho_name)) +
  geom_tile(aes(alpha = percent_of_sample, fill = morpho_sp)) + # color = "white" %>% fct_reorder(morpho_order)
  labs(x="Cell morphology", y= "Elevation", fill = "Cell morphology", alpha="Relative abundance") +
  scale_alpha(range = c(0.1, 1)) +
  my_theme

@@

@@

```{r}
dir.create(here("manuscript/figs/supp/cellct"))
ggsave(filename=here("manuscript/figs/supp/cellct/cellct_heatmap.pdf"), plot=cellct_heatmap, height = 7, width = 3)
ggsave(here("manuscript/figs/supp/cellct/elevations.pdf"), plot=elev, height=7, width=1)
```

>>>>

```{r heatmap, echo=F, fig.height=5, fig.width=6}
cellct_tbl <- cellct %>% 
  left_join(field, by="sample_id")

distinct(cellct_tbl, sample_id) %>% nrow()
```

Heatmap for figure 4
```{r, echo=F, fig.height=5, fig.width=6}

cellct_tbl_w_seq <- cellct_tbl %>% 
  filter(sample_id %in% samples_w_seq)

samples_w_seq ## not sure where this comes from
samples_with_cellcounts <- cellct_tbl_w_seq %>% distinct(sample_id) %>% pull(sample_id)
setdiff(samples_w_seq, samples_with_cellcounts) # missing these

cellct_tbl_w_seq %>% distinct(sample_id)
cellct_tbl_w_seq %>% distinct(morpho_sp)

my_theme <- theme(axis.text.x = element_text(angle = 45, hjust = 1))

cellct_ord <- c("Chlainomonas rubra","Sanguina nivaloides","Chloromonas krienitzii","Chloromonas cf. brevispina","Chloromonas cf. nivalis", "Green cell","Other")

cellct_tbl_w_seq %>% distinct(sample_id) %>% nrow()

cellct_heatmap <- ggplot(cellct_tbl_w_seq, 
                         aes(y=alias %>% fct_reorder(elev_m), 
                             x=morpho_sp %>% fct_relevel(cellct_ord))) +
  geom_tile(aes(alpha = percent_of_sample, fill = morpho_sp %>% fct_relevel(cellct_ord))) +
  labs(x="Cell morphology", y= "Elevation") +
  scale_alpha(range = c(0.1, 1)) +
  my_theme +
  guides(alpha="none",fill="none")

@@

```{r, echo=F, fig.height=5, fig.width=6}

my_theme <- theme(axis.text.y=element_blank(),
                  axis.ticks.y=element_blank())

p2 <- p %>% 
 filter(!(morpho_sp %in% c("Other","Green cell")))
cellct_scatter <- ggplot(p2, aes(x=date, y=elev_m)) +
  geom_jitter(aes(color=morpho_sp, size=percent_of_sample), alpha=0.5, width = 10, height=10) +
  scale_size(range=c(0.5, 10)) +
  labs(color="Morphospecies",size="Relative abundance",y="Elevation (m)",x="Date") +
  guides(colour = guide_legend(override.aes = list(alpha = 1, size=3))) +
  ggthemes::theme_few()
cellct_scatter

# pie charts?
```

@@

```{r}
# dir.create(here("manuscript/figs/supp/cellct"))
ggsave(filename=here("manuscript/figs/supp/cellct/cellct_dotplot.pdf"), plot=cellct_scatter, height = 5, width = 6)
ggsave(here("manuscript/figs/supp/cellct/elevations.pdf"), plot=elev, height=7, width=1)

saveRDS(cellct_heatmap, here("output/cellct_w_seq_heatmap.Rda"))
```
